Visualizations for the manuscript

### 2022-05-13 metanalysis_visualization/manuscript_Figures.Rmd
bootstrap number changing

```{r}
# Call function from another file : bootstrap.R
bootstrap_size <- 100
binom_proportion <- function(n, prob, size) {
  (rbinom(n, size, prob) / size) * 100
}

>>>>

```{r}
# Call function from another file : bootstrap.R
bootstrap_size <- 10000
binom_proportion <- function(n, prob, size) {
  (rbinom(n, size, prob) / size) * 100
}
